Figures to insert in text

### 2018-04-03 kanerva-answer.tex
toying around with text

This is an important insight: a hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes' to write on its own corresponding bit-address more than it likes the opposite; as each hard-location has a say in its own area (and nowhere else).

@@

THIS STEP IS A LITTLE WTF TO ME...

$\frac{n-k}{n} \binom{n}{k} = \frac{n-k}{n} \binom{n}{n-k} = \frac{n-k}{n} \frac{n!}{k!(n-k)!}$ \\

$ = \frac{(n-k)(n-1)!}{k!(n-k)!} $

$ = \frac{(n-1)!}{k!(n-k-1)!}$

>>>>

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes' to write on its own corresponding bit-address more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.

@@
